Accelerating Precision Medicine with Quantum Computing and AI\\\bigskip \LARGE\mdseries\itshape\color{black!80} Exploring the future of Personalized Health Care\par

### 2022-01-23 paper.tex
(paper/bibliography) setup citation processor, adjust formatting

% Created 2022-01-23 Sun 02:57
% Intended LaTeX compiler: pdflatex
\documentclass{scrartcl}
\renewcommand\sectionformat{\llap{\thesection\autodot\enskip}}
\renewcommand\subsectionformat{\llap{\thesubsection\autodot\enskip}}
\renewcommand\subsubsectionformat{\llap{\thesubsubsection\autodot\enskip}}

@@

\author{Shaurya Singh}
\date{\today}
\title{Accelerating Precision Medicine with Quantum Computing and AI\\\bigskip
\LARGE\mdseries\itshape\color{black!80} Exploring the future of Personalized Health Care\par}
\colorlet{greenyblue}{blue!70!green}
\colorlet{blueygreen}{blue!40!green}
\providecolor{link}{named}{greenyblue}
\providecolor{cite}{named}{blueygreen}
\hypersetup{
  pdfauthor={Shaurya Singh},
  pdftitle={Accelerating Precision Medicine with Quantum Computing and AI},
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs 29.0.50 (Org mode 9.6)},
  pdflang={English},
  breaklinks=true,
  colorlinks=true,
  linkcolor=,
  urlcolor=link,
  citecolor=cite
}
\urlstyle{same}
\usepackage{biblatex}
\addbibresource{/Users/shauryasingh/Projects/qML-PM/paper.bib}
\begin{document}

@@

\begin{itemize}
\item \textbf{Keywords:} Quantum Computing, Artificial intelligence, Precision Medicine
\item \textbf{Environment:} \href{https://www.gnu.org/software/emacs/}{Emacs} 29.0, \href{https://www.gnu.org/software/emacs/}{Org mode} 9.6 \& \href{https://www.python.org/}{Python} 3.9.10
\item \textbf{License:} MIT
\end{itemize}
\end{abstract}

@@

\section{Introduction}
\label{sec:org5350abb}

Healthcare data—such as information from clinical trials, disease registries, electronic health records (EHRs), and medical devices—is growing at a compound annual growth rate of 36 percent. Increasingly, this data helps address 4 challenges associated with healthcare

@@

Significant investments are being made to deliver the right data and powerful insights at the point of care. Industry incumbents and new entrants alike are trying to create digital experiences that reinforce healthy, preventive behaviors. Despite that, accounting for the exponential possibilities from this diversity of new data is stretching the capabilities of classical computing systems.

\section{AI in Precision Medicine}
\label{sec:orgee2425f}

@@

\subsection{Accelerating AI with Quantum Computing}
\label{sec:org7486d72}

@@

\subsection{Hybrid Quantum-Classical Neural Networks}
\label{sec:orgd332638}

@@

\subsection{Generative Adversarial Networks}
\label{sec:orgc118b07}

@@

\subsubsection{MolGAN}
\label{sec:orgb6ea8c1}

@@

\subsubsection{Qubit-efficient Quantum Molecule Generation}
\label{sec:orgf04309c}

@@

\section{Prototype}
\label{sec:org028f6e9}

@@

\subsection{Image recognition (QuTorch-HG)}
\label{sec:org40cc62b}

@@

\subsection{Quantum Accelerated Drug \& Molecule Generation (QGAN-HG)}
\label{sec:org978dc50}

@@

\subsection{Data}
\label{sec:org3b37fd2}

@@

\subsection{Tools and Hardware}
\label{sec:org9017251}

@@

While simulated hardware produces \emph{slightly} different results to actual hardware, the margin is within 1\%. The tests below were conducted using actual IBMQ hardware, on the \verb~ibmq_lima~ quantum computer.

@@

\section{Results}
\label{sec:org564a799}

\subsection{Speed}
\label{sec:org2d16445}

@@

\subsection{Accuracy}
\label{sec:orgd615ad4}

@@

\subsection{Pricing}
\label{sec:org1ac401b}

@@

\section{Conclusion and Further Research}
\label{sec:org16f8dc5}

\section{References}
\label{sec:org6f3443d}

\printbibliography

>>>>

% Created 2022-01-23 Sun 13:16
% Intended LaTeX compiler: pdflatex
\documentclass{scrartcl}
\renewcommand\sectionformat{\llap{\thesection\autodot\enskip}}
\renewcommand\subsectionformat{\llap{\thesubsection\autodot\enskip}}
\renewcommand\subsubsectionformat{\llap{\thesubsubsection\autodot\enskip}}

@@

\author{Shaurya Singh}
\date{\today}
\title{Accelerating Precision Medicine with Quantum Computing and AI\\\bigskip
\LARGE\mdseries\itshape\color{black!80} Exploring the future of Personalized Health Care\par}
\colorlet{greenyblue}{blue!70!green}
\colorlet{blueygreen}{blue!40!green}
\providecolor{link}{named}{greenyblue}
\providecolor{cite}{named}{blueygreen}
\hypersetup{
  pdfauthor={Shaurya Singh},
  pdftitle={Accelerating Precision Medicine with Quantum Computing and AI},
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs 29.0.50 (Org mode 9.6)},
  pdflang={English},
  breaklinks=true,
  colorlinks=true,
  linkcolor=,
  urlcolor=link,
  citecolor=cite
}
\urlstyle{same}
\makeatletter
\newcommand{\citeprocitem}[2]{\hyper@linkstart{cite}{citeproc_bib_item_#1}#2\hyper@linkend}
\makeatother

\usepackage[notquote]{hanging}
\begin{document}

@@

\begin{itemize}
\item \textbf{Keywords:} Quantum Computing, Artificial intelligence, Precision Medicine
\item \textbf{Environment:}
\item \textbf{License:} MIT
\end{itemize}
\end{abstract}

@@

\section{Introduction}
\label{sec:org3746fb1}

Healthcare data—such as information from clinical trials, disease registries, electronic health records (EHRs), and medical devices—is growing at a compound annual growth rate of 36 percent  . Increasingly, this data helps address 4 challenges associated with healthcare:

@@

Significant investments are being made to deliver the right data and powerful insights at the point of care. Industry incumbents and new entrants alike are trying to create digital experiences that reinforce healthy, preventive behaviors. Despite that, accounting for the exponential possibilities from this diversity of new data is stretching the capabilities of classical computing systems. [\citeprocitem{1}{Grumbling and Horowitz 2020}].

\section{AI in Precision Medicine}
\label{sec:orgaa38e6b}

@@

\subsection{Accelerating AI with Quantum Computing}
\label{sec:org5f9b1a5}

@@

\subsection{Hybrid Quantum-Classical Neural Networks}
\label{sec:org4513971}

@@

\subsection{Generative Adversarial Networks}
\label{sec:org4a73d5d}

@@

\subsubsection{MolGAN}
\label{sec:org6af9af7}

@@

\subsubsection{Qubit-efficient Quantum Molecule Generation}
\label{sec:org3384f98}

@@

\section{Prototype}
\label{sec:orgc2eb20e}

@@

\subsection{Image recognition (QuTorch-HG)}
\label{sec:orgb83bbdc}

@@

\subsection{Quantum Accelerated Drug \& Molecule Generation (QGAN-HG)}
\label{sec:org76ff07f}

@@

\subsection{Data}
\label{sec:org25dde5d}

@@

\subsection{Tools and Hardware}
\label{sec:orgdbffe93}

@@

While simulated hardware produces \emph{slightly} different results to actual hardware, the margin is within 1\%. The tests below were conducted using actual IBMQ hardware, on the \verb~ibmq_lima~ quantum computer [\citeprocitem{2}{Quantum 2021}]

@@

\section{Results}
\label{sec:orga8ccec7}

\subsection{Speed}
\label{sec:orgfc5ab1f}

@@

\subsection{Accuracy}
\label{sec:org8b71621}

@@

\subsection{Pricing}
\label{sec:org2502bef}

@@

\section{Conclusion and Further Research}
\label{sec:org1f114d9}

\section{References}
\label{sec:orgddb3177}

\begin{hangparas}{1.5em}{1}
\hypertarget{citeproc_bib_item_1}{\textsc{Grumbling, E. and Horowitz, M.} 2020. \href{https://doi.org/10.17226/25196}{Quantum computing}. .}

\hypertarget{citeproc_bib_item_2}{\textsc{Quantum, I.} 2021. \href{https://quantum-computing.ibm.com/}{Ibm quantum services}. .}
\end{hangparas}
